---
title: "Task-3: Iris Flower Classification"
author: "Kankana Ghosh"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

Importing all the necessary libraries required for the analysis.
```{r setup, include=TRUE}

rm(list=ls())
library(MASS)
library(klaR)
library(clusterSim)
library(GGally)
library(ggpubr)
df=iris
class(df)
str(df)
```

**Comments:**
The dataset Iris is a dataframe in nature consisting 150 observations on 5 variables. The variable Species is categorical in nature having "Setosa", "versicolor" and "virginica" corresponding to which there are four variables taking measurements on it's Sepal Length, Sepal Width, Petal Length and Petal Width.

```{r}
ggpairs(df,columns = 1:4,ggplot2::aes(colour=Species))+ggtitle("Pairplot with respect to different species")+
  theme(plot.title = element_text(hjust=0.5))
```

**Comments:**
From the pairplot we get the idea of the correlation between different measurements of the 3 species.
```{r}
ggplot(data=df,aes(x=Sepal.Length,fill=factor(Species)))+geom_boxplot()+scale_fill_discrete(name="Species")+
  coord_flip()+ylab("Species")+ggtitle("Boxplot for Sepal Length across Species")+
  theme(plot.title = element_text(hjust=0.5))

ggplot(data=df,aes(x=Sepal.Width,fill=factor(Species)))+geom_boxplot()+scale_fill_discrete(name="Species")+
  coord_flip()+ylab("Species")+ggtitle("Boxplot for Sepal Width across Species")+
  theme(plot.title = element_text(hjust=0.5))

ggplot(data=df,aes(x=Petal.Length,fill=factor(Species)))+geom_boxplot()+scale_fill_discrete(name="Species")+
  coord_flip()+ylab("Species")+ggtitle("Boxplot for Petal Length across Species")+
  theme(plot.title = element_text(hjust=0.5))

ggplot(data=df,aes(x=Petal.Width,fill=factor(Species)))+geom_boxplot()+scale_fill_discrete(name="Species")+
  coord_flip()+ylab("Species")+ggtitle("Boxplot for Petal Width across Species")+
  theme(plot.title = element_text(hjust=0.5))
```

**Comments:**
From the boxplot for Sepal Length across species it is clear that the Sepal Length of the specie virginica is more compared to the other two species.Virginica has outlier present in them.

From the boxplot for Sepal Width across species it is clear that the Sepal Width of the specie setosa is more compared to the other two species.Virginica and setosa has outlier present in them.

From the boxplot for Petal Length across species it is clear that the Petal Length of the specie virginica is more compared to the other two species.Versicolor and setosa has outlier present in them.

From the boxplot for Petal Width across species it is clear that the Petal Width of the specie virginica is more compared to the other two species.Setosa has outlier present in them.

```{r}
a=ggplot(data=df,aes(x=Sepal.Length))+geom_boxplot(aes(Sepal.Length),fill="lightblue")+coord_flip()
b=ggplot(data=df,aes(x=Sepal.Width))+geom_boxplot(aes(Sepal.Width),fill="red")+coord_flip()
d=ggplot(data=df,aes(x=Petal.Length))+geom_boxplot(aes(Petal.Length),fill="lightpink")+coord_flip()
e=ggplot(data=df,aes(x=Petal.Width))+geom_boxplot(aes(Petal.Width),fill="orange")+coord_flip()
plot=ggarrange(a,b,d,e)
annotate_figure(plot,top=text_grob("Boxplot for Predictors",face="bold",size=14))

apply(df[,-5], 2,mean)
apply(df[,-5], 2,var)
apply(df[,-5], 2,median)
```

Splitting the dataset into train and test data in the ratio of 80:20.
```{r}
s=sample(c(TRUE,FALSE),nrow(df),replace=TRUE,c(0.8,0.2))
train=df[s,]
test=df[!s,]
model=lda(Species~.,data=train)
model

pred=predict(model,newdata =  test)
pred

mean(pred$class==test$Species)

df.standard=data.Normalization(df[,-5],type="n1")
Species=df[,5]
df1=cbind(Species,df.standard)
partimat(Species~.,data = df1,method="lda")

```

**Comments:**
Now to classify iris flowers into different species based on their sepal and petal measurements I have used the LDA model. Fitting the model on the train dataset I got the prior probabilities as 0.35,0.34,0.30 for setosa, versicolor and virginica respectively.It means that the chance to classify a specie into setosa, versicolor and virginica is the above mentioned probabilities.Here, we get two discriminants hence the linear combinations of the predictors (i.e, the four measurements) that are used to form the LDA decision rule are:

LD1=0.70* Sepal.Length + 1.40* Sepal.Width - 2.25* Petal.Length - 2.39* Petal.Width
LD2=-0.54* Sepal.Length + 2.19* Sepal.Width - 0.72* Petal.Length + 2.88* Petal.Width

The accuracy of this model is coming out to be 1, hence the above model is a perfect model, i.e., the above decision rules can correctly classify a specie based on the different measurements.

From the partition plot we get an idea of the classification of the species into three regions. In each case we get the approximate error rate which indicates the incorrect classification.

